Metropolitan Statistical Area Evaluation

### 2022-11-29 src/demo_data_wrangling.Rmd
double checking change in emp rate

>>>>

avg_emp_change <- MSA_employment %>% 
  group_by(MSA, year) %>% 
  summarize(avg_employment_rate = mean(employment_rate)) %>% 
  pivot_wider(names_from = year,
              values_from = avg_employment_rate,
              names_prefix = "emp_rate") %>% 
  mutate(emp_change20_21 = (emp_rate2021 - emp_rate2020) /emp_rate2020 *100) %>% 
  full_join(avg_emp_yoy) %>% 
  filter(year == "2021")
